---
output: 
  flexdashboard::flex_dashboard:
    theme: flatly
    logo: ~/Downloads/6AMHealth/Logo.png
    orientation: rows
runtime: shiny
---

```{r}
library(flexdashboard)
library(knitr)
library(DT)
library(rpivotTable)
library(ggplot2)
library(plotly)
library(dplyr)
library(openintro)
library(highcharter)
library(gsheet)
library(data.table)
library(zoo)
library(gsheet)
library(shiny)
library(tidyverse)
library(scales)
```


```{r}

url = 'https://docs.google.com/spreadsheets/d/1_8CvwhQM9vK5AWr3Jkn64b_5pH78NKNSwak2WnYNd4o/edit?usp=sharing'
url2 = 'https://docs.google.com/spreadsheets/d/1_8CvwhQM9vK5AWr3Jkn64b_5pH78NKNSwak2WnYNd4o/edit#gid=613274356'
df = fread(text = gsheet2text(url, format = 'csv'), stringsAsFactors = FALSE)
df$Date <- as.Date(df$Date, "%m/%d/%Y")
df$Kiosk <- as.character(df$Kiosk) 
df$DateTime <- as.POSIXct(paste(df$Date, df$Time), format = "%Y-%m-%d %I:%M:%S %p")

last_seven_days = subset(df,Date >= as.Date(max(df$Date),format='%Y-%m-%d')-6)
number_of_fridge_active <- length(unique(df$Kiosk))


info <- fread(text = gsheet2text(url2, format = 'csv'), stringsAsFactors = FALSE)
info <- info%>%select(Kiosk:`Food Waste %`)
info <- drop_na(info)
```

Daily Reports 
=======================================================================

Row {.tabset .tabset-fade}
-------------------------------------

```{r, echo=FALSE, message=FALSE}
#create the dates to be in the table 
top_date  = as.Date(max(df$Date),format='%Y-%m-%d')
low_date  = top_date-6
dts_      = seq.Date(low_date, top_date,by="day")
daterange = dts_[rev(order(as.Date(dts_, format = "%m-%d-%Y")))]

#Create a list that contains the data sliced into 7 dataframes in order to calculate 
#7 different 7-day averages 
my_sales = list()
p = 1
for (i in daterange){
  sliced = subset(df, Date >= (as.Date(i, origin="1970-01-01")-6) & Date <= as.Date(i, origin="1970-01-01"))
  my_sales[[p]] = sliced
  p = p+1
}

rolling_stats = as.data.frame(matrix(c("ARS", "Byte", "Total","ARS Avg.Units Sold per Fridge",
                   "Byte Avg.Units Sold per Fridge","Combined Avg. Units Sold per Fridge"), ncol = 1, nrow = 6))

for (i in seq(1:7)){
  rolling      = my_sales[[i]]
  edited_7days = rolling %>% select(Date, Total, Qty, Fridge_Type) %>% group_by(Fridge_Type,Date) %>%
                              summarise(Sales = sum(Total),Units_Sold = sum(Qty)) %>% 
                              group_by(Date, Fridge_Type) %>% summarise(Total = sum(Units_Sold))
  #create the dates to be in the table 
  max_date     = as.Date(max(edited_7days$Date),format='%Y-%m-%d')
  min_date     = max_date-6
  dts_seq      = seq.Date(min_date, max_date,by="day")
  datelist     = dts_seq[rev(order(as.Date(dts_seq, format = "%m-%d-%Y")))]
  edited_wide  = spread(edited_7days,Date,Total)
  edited_wide[is.na(edited_wide)] = 0
  total_row    = c("Total",colSums(edited_wide[,2:8]))
  edited_wide  = rbind(edited_wide,total_row)
  edited_wide  = edited_wide %>% mutate_at(2:8, as.integer)
  Weekly       = c(rowSums(edited_wide[,2:8])/7)
  edited_wide  = cbind(edited_wide,Weekly)
  edited_wide  = edited_wide[,c(1,9,8,7,6,5,4,3,2)]
  colnames(edited_wide) = c("Fridge Type", "Weekly Avg.", paste(weekdays(datelist),datelist,sep = " "))
  edited_wide  = edited_wide %>% mutate_at(2:8, as.integer)
  
  #The next three variables store the total number of fridges active in the last 7 days 
  n_fridges    = rolling %>% summarise(n_distinct(Kiosk))
  n_Byte       = rolling %>% filter(Fridge_Type=="Byte") %>% summarise(n_distinct(Kiosk))
  n_ARS        = rolling %>% filter(Fridge_Type=="ARS") %>% summarise(n_distinct(Kiosk))
  
  ARS_row      = round(edited_wide[which(edited_wide[,1]=="ARS"),2:9]/sum(n_ARS),2)
  Byte_row     = round(edited_wide[which(edited_wide[,1]=="Byte"),2:9]/sum(n_Byte),2)
  Total_row    = round(edited_wide[which(edited_wide[,1]=="Total"),2:9]/sum(n_fridges),2)
  edited_wide  = bind_rows(edited_wide,ARS_row,Byte_row,Total_row)
  edited_wide[4:6,1] = c("ARS Avg. Units Sold per Fridge","Byte Avg. Units Sold per Fridge","Combined Avg. Units Sold per Fridge")
  rolling_stats= cbind(rolling_stats, edited_wide$`Weekly Avg.`)
}
colnames(rolling_stats) = c("Metrics", paste(weekdays(daterange),daterange,sep = " "))
```

### Last 7 days 
The first column tells  you the fridge type.

The second column shows you the amount of active fridges in the last 7 days.

The third column tells you the Avg. dollar price point per unit per fridge type of the last 7 days.

The fourth column represents the Avg. price point per unit sold of over the last 7 days

```{r, echo=FALSE, fig.width=10, fig.height=7}
#this is for the first table 
last_seven_days = subset(df,Date >= as.Date(max(df$Date),format='%Y-%m-%d')-6)
n_fridges = last_seven_days %>% summarise(n_distinct(Kiosk))
n_Byte    = last_seven_days %>% filter(Fridge_Type=="Byte") %>% summarise(n_distinct(Kiosk))
n_ARS     = last_seven_days %>% filter(Fridge_Type=="ARS") %>% summarise(n_distinct(Kiosk))
#this stores all three previous values into a single vector 
Fridges   = unname(c(n_ARS,n_Byte,n_fridges))

grouped_7days = last_seven_days %>% group_by(Fridge_Type) %>% summarise(Sales = sum(Total),
                                                                        Units = sum(Qty))
grouped_7days = rbind(grouped_7days, c("Total", colSums(grouped_7days[,2:3])))
grouped_7days = grouped_7days %>% mutate_at(2:3, as.integer)
column2       = cbind(grouped_7days$Fridge_Type,c(round(grouped_7days$Sales/grouped_7days$Units,2)))
column1       = rolling_stats[4:6,1:2] 
first_T       = cbind(column2[,1],Fridges, column1[,2],column2[,2])
first_T_colnames = c("Fridge Type","Amount", "Avg. Units Sold Per Fridge", "Avg. Price per Unit")
colnames(first_T) = first_T_colnames

first_T[,4] = paste("$", first_T[,4], sep = "")
datatable(first_T, filter = "top", options = list(pageLength = nrow(first_T), autoWidth=TRUE))
```

### Last 7 days Units Rolling Averages
Each column contains the weekly average of units sold for the past 7 days for everyday in the past week
```{r, echo=FALSE, message=FALSE}
#use the datatable() function from the formattable package 
datatable(rolling_stats, filter = "top", options = list(pageLength = nrow(rolling_stats), autoWidth=TRUE))
```

### Last 7 days Sales Rolling Averages
Each column contains the weekly average of sales made for the past 7 days for everyday in the past week

```{r, echo=FALSE, message=FALSE}
#create the dates to be in the table 
top_date  = as.Date(max(df$Date),format='%Y-%m-%d')
low_date  = top_date-6
dts_      = seq.Date(low_date, top_date,by="day")

daterange = dts_[rev(order(as.Date(dts_, format = "%m-%d-%Y")))]

#Create a list that contains the data sliced into 7 dataframes in order to calculate 
#7 different 7-day averages 
my_sales = list()
p = 1
for (i in daterange){
  sliced = subset(df, Date >= (as.Date(i, origin="1970-01-01")-6) & Date <= as.Date(i, origin="1970-01-01"))
  my_sales[[p]] = sliced
  p = p+1
}

rolling_stats = as.data.frame(matrix(c("ARS", "Byte", "Total","ARS Avg. Dollar Sales per Fridge",
                   "Byte Avg. Dollar Sales per Fridge","Combined Avg. Dollar Sales per Fridge"), ncol = 1, nrow = 6))

for (i in seq(1:7)){
  rolling      = my_sales[[i]]
  edited_7days = rolling %>% select(Date, Total, Qty, Fridge_Type) %>% group_by(Fridge_Type,Date) %>%
                              summarise(Sales = sum(Total),Units_Sold = sum(Qty)) %>% 
                              group_by(Date, Fridge_Type) %>% summarise(Total = sum(Sales))
  #create the dates to be in the table 
  max_date     = as.Date(max(edited_7days$Date),format='%Y-%m-%d')
  min_date     = max_date-6
  dts_seq      = seq.Date(min_date, max_date,by="day")
  datelist     = dts_seq[rev(order(as.Date(dts_seq, format = "%m-%d-%Y")))]
  edited_wide  = spread(edited_7days,Date,Total)
  edited_wide[is.na(edited_wide)] = 0
  total_row    = c("Total",colSums(edited_wide[,2:8]))
  edited_wide  = rbind(edited_wide,total_row)
  edited_wide  = edited_wide %>% mutate_at(2:8, as.integer)
  Weekly       = c(rowSums(edited_wide[,2:8])/7)
  edited_wide  = cbind(edited_wide,Weekly)
  edited_wide  = edited_wide[,c(1,9,8,7,6,5,4,3,2)]
  colnames(edited_wide) = c("Fridge Type", "Weekly Avg.", paste(weekdays(datelist),datelist,sep = " "))
  edited_wide  = edited_wide %>% mutate_at(2:8, as.integer)
  
  #The next three variables store the total number of fridges active in the last 7 days 
  n_fridges    = rolling %>% summarise(n_distinct(Kiosk))
  n_Byte       = rolling %>% filter(Fridge_Type=="Byte") %>% summarise(n_distinct(Kiosk))
  n_ARS        = rolling %>% filter(Fridge_Type=="ARS") %>% summarise(n_distinct(Kiosk))
  
  ARS_row      = round(edited_wide[which(edited_wide[,1]=="ARS"),2:9]/sum(n_ARS),2)
  Byte_row     = round(edited_wide[which(edited_wide[,1]=="Byte"),2:9]/sum(n_Byte),2)
  Total_row    = round(edited_wide[which(edited_wide[,1]=="Total"),2:9]/sum(n_fridges),2)
  edited_wide  = bind_rows(edited_wide,ARS_row,Byte_row,Total_row)
  edited_wide[4:6,1] = c("ARS Avg. Dollar Sales per Fridge","Byte Avg. Dollar Sales per Fridge","Combined Avg. Dollar Sales per Fridge")
  rolling_stats= cbind(rolling_stats, edited_wide$`Weekly Avg.`)
}

colnames(rolling_stats) = c("Metrics", paste(weekdays(daterange),daterange,sep = " "))
```

```{r, echo=FALSE, message=FALSE}
my_copy = data.frame(rolling_stats)
for (i in 2:8){
  for (b in 1:6){
    rolling_stats[b,i] = paste("$", rolling_stats[b,i], sep = "")
  }
}
#use the datatable() function from the formattable package 
datatable(rolling_stats, filter = "top", options = list(pageLength = nrow(rolling_stats), autoWidth=TRUE))
```

Sales
=======================================================================


Inputs {.sidebar data-width=200}
-----------------------------------------------------------------------

```{r}
selectInput('Kiosk', 'Select a kiosk', unique(df$Kiosk))
```

* Use ‘Select a kiosk’ sidebar to select ONE kiosk.  
* Please refer to 'About' if you have any questions. 


Row
-----------------------------------------------------------------------
### Days Active
    
```{r}
selectedData <- reactive({
  df %>% filter(df$Kiosk == input$Kiosk)
})

days <- reactive({
  startDate = min(selectedData()$Date)
  daysOperational = Sys.Date()-startDate
})



#valueBox(value = days$daysOperational, icon = "fa-pencil")
renderValueBox({
  daysactive <- formatC(days(),  digits = 0, format = 'f')
  valueBox(
    value = daysactive
  )
})


```

### Units Sold to Date
```{r}
selectedData <- reactive({
  df %>% filter(df$Kiosk == input$Kiosk)
})

units_sold <- reactive({
  selectedData()%>%summarise(Units_Sold = sum(Qty))
})

renderValueBox({
  units <- formatC(units_sold()$Units_Sold,  digits = 0, format = 'f')
  valueBox(
    value = units
  )
})
```

### Dollar Sales to Date
```{r}
selectedData <- reactive({
  df %>% filter(df$Kiosk == input$Kiosk)
})

Dollar_Sales <- reactive({
  selectedData()%>%summarise(Dollar_Sales = sum(Total))
})

renderValueBox({
  dollars <- paste0("$",formatC(Dollar_Sales()$Dollar_Sales,  digits = 2, format = 'f'))
  valueBox(
    value = dollars
  )
})
```

### Historical Units Sold Per Day (Since Inception)
```{r}
selectedData <- reactive({
  df %>% filter(df$Kiosk == input$Kiosk)
})

Unit_Sold_Per_Day <- reactive({
  selectedData()%>%summarise(Unit_Sold_Per_Day = sum(Qty)/as.numeric(days(), units='days'))
})

renderValueBox({
  unitsperday <- formatC(Unit_Sold_Per_Day()$Unit_Sold_Per_Day,  digits = 2, format = 'f')
  valueBox(
    value = unitsperday
  )
})
```


### Historical Average Unit Price (Since Inception)
```{r}
selectedData <- reactive({
  df %>% filter(df$Kiosk == input$Kiosk)
})

Historical_Average_Unit_Price <- reactive({
  selectedData()%>%summarise(Historical_Average_Unit_Price = sum(Total)/sum(Qty))
})

renderValueBox({
  salesperdate <- paste0("$",formatC(Historical_Average_Unit_Price()$Historical_Average_Unit_Price,  digits = 2, format = 'f'))
  valueBox(
    value = salesperdate
  )
})
```

### Average Daily Units Sold Last Week 
```{r}
sevendaysselectedData <- reactive({
  last_seven_days %>% filter(last_seven_days$Kiosk == input$Kiosk)
})

seven_days_running_average_unit_sales <- reactive({
  sevendaysselectedData()%>%summarise(seven_days_average = sum(Qty)/7)
})

renderValueBox({
  running_average_unit_sales <- formatC(seven_days_running_average_unit_sales()$seven_days_average,  digits = 2, format = 'f')
  valueBox(
    value = running_average_unit_sales
  )
})
```

### Average Daily Dollar Sales Past Week 
```{r}
sevendaysselectedData <- reactive({
  last_seven_days %>% filter(last_seven_days$Kiosk == input$Kiosk)
})

seven_days_running_average_dollar_sales <- reactive({
  sevendaysselectedData()%>%summarise(seven_days_dollar_average = sum(Total)/7)
})

renderValueBox({
  running_average_dollar_sales <- paste0('$',formatC(seven_days_running_average_dollar_sales()$seven_days_dollar_average,  digits = 2, format = 'f'))
  valueBox(
    value = running_average_dollar_sales
  )
})
```

### Average Unit Price Past 7 Days
```{r}
sevendaysselectedData <- reactive({
  last_seven_days %>% filter(last_seven_days$Kiosk == input$Kiosk)
})

seven_days_average_price <- reactive({
  sevendaysselectedData()%>%summarise(seven_days_average_price = sum(Total)/sum(Qty))
})

renderValueBox({
  running_average_unit_price<- paste0('$',formatC(seven_days_average_price()$seven_days_average_price,  digits = 2, format = 'f'))
  valueBox(
    value = running_average_unit_price
  )
})
```


Row {.tabset .tabset-fade}
-------------------------------------

### Average Unit Price by Week
```{r}

selectedData <- reactive({
  df %>% filter(df$Kiosk == input$Kiosk)
})

Avg_Unit_Price <- reactive({selectedData()%>%group_by(week(Date))%>%summarise(AvgUnitPrice=sum(Total)/sum(Qty))
  })

overall <- reactive({df%>%group_by(week(Date))%>%summarise(avgUnitPrice=sum(Total)/sum(Qty))%>%
    filter(`week(Date)`%in%Avg_Unit_Price()$`week(Date)`)})

fridgetypeAverage <- reactive({
  df %>% filter(Fridge_Type == selectedData()$Fridge_Type[1])%>%group_by(week(Date))%>%summarise(avgUnitPrice=sum(Total)/sum(Qty))%>%
    filter(`week(Date)`%in%Avg_Unit_Price()$`week(Date)`)
})


renderPlotly(plot_ly(Avg_Unit_Price(), x=~`week(Date)`, y=~AvgUnitPrice,name=input$Kiosk,type = 'scatter', mode = 'lines',line=list(color = '#2ca02c'))%>%add_trace(y=~overall()$avgUnitPrice,name='6AM Average',mode = "lines",line=list(dash='dot',color='blue'))%>%add_trace(y=~fridgetypeAverage()$avgUnitPrice, name = paste0(selectedData()$Fridge_Type[1],' Average'), mode = 'lines', line = list(dash='dot',color='#d62728'))%>%
  layout(title = "Average Unit Price by Week",
         paper_bgcolor='rgb(255,255,255)', plot_bgcolor='rgb(229,229,229)',
         xaxis = list(title = "Week",
                      gridcolor = 'rgb(255,255,255)',
                      showgrid = TRUE,
                      showline = FALSE,
                      showticklabels = TRUE,
                      tickcolor = '#2ca02c',
                      ticks = 'outside',
                      zeroline = FALSE),
         yaxis = list(title = "Average Unit Price",
                      gridcolor = 'rgb(255,255,255)',
                      showgrid = TRUE,
                      showline = FALSE,
                      showticklabels = TRUE,
                      tickcolor = '#2ca02c',
                      ticks = 'outside',
                      zeroline = TRUE)))
```

### Average Units Sold Per Day
```{r}
AvgUnitSold <- reactive({selectedData()%>%group_by(week(Date))%>%summarise(AvgUnitSold=sum(Qty)/length(unique(Date)))
  })


number_of_fridge_active <- reactive({df %>% group_by(week(Date))%>%filter(`week(Date)`%in%AvgUnitSold()$`week(Date)`)%>%summarise(numberFridge = length(unique(Kiosk)))})

overall1 <- reactive({df%>%group_by(week(Date))%>%summarise(AvgUnitSold=sum(Qty)/length(unique(Date)))%>%
    filter(`week(Date)`%in%AvgUnitSold()$`week(Date)`)})
overallAverage <- reactive({overall_average = overall1()$AvgUnitSold/number_of_fridge_active()$numberFridge})

number_of_fridge_active_fridge_type <- reactive({df %>% filter(Fridge_Type==selectedData()$Fridge_Type[1])%>% group_by(week(Date))%>%filter(`week(Date)`%in%AvgUnitSold()$`week(Date)`)%>%summarise(numberFridge = length(unique(Kiosk)))})
fridgetypeAverage1 <- reactive({df%>%group_by(week(Date))%>%filter(Fridge_Type==selectedData()$Fridge_Type[1])%>%summarise(AvgUnitSold=sum(Qty)/length(unique(Date)))%>%filter(`week(Date)`%in%AvgUnitSold()$`week(Date)`)})
fridgetypeAverage11 <- reactive({overall_average = fridgetypeAverage1()$AvgUnitSold/number_of_fridge_active_fridge_type()$numberFridge})

renderPlotly(plot_ly(AvgUnitSold(), x=~`week(Date)`, y=~AvgUnitSold,name=input$Kiosk, type = 'scatter', mode = 'lines',line=list(color = '#2ca02c'))%>%add_trace(y=~overallAverage(), name='6AM Average',mode = "lines",line=list(dash='dot',color='blue'))%>%add_trace(y=~fridgetypeAverage11(), name = paste0(selectedData()$Fridge_Type[1],' Average'), mode = 'lines', line = list(dash='dot',color='#d62728'))%>%
  layout(title = "Average Units Sold Per Day",
         paper_bgcolor='rgb(255,255,255)', plot_bgcolor='rgb(229,229,229)',
         xaxis = list(title = "Week",
                      gridcolor = 'rgb(255,255,255)',
                      showgrid = TRUE,
                      showline = FALSE,
                      showticklabels = TRUE,
                      tickcolor = '#2ca02c',
                      ticks = 'outside',
                      zeroline = FALSE),
         yaxis = list(title = "Average Unit Sold",
                      gridcolor = 'rgb(255,255,255)',
                      showgrid = TRUE,
                      showline = FALSE,
                      showticklabels = TRUE,
                      tickcolor = '#2ca02c',
                      ticks = 'outside',
                      zeroline = TRUE)))
```

### Average Dollar Sales Per Day
```{r}
AvgTotalSold <- reactive({selectedData()%>%group_by(week(Date))%>%summarise(AvgTotalSold=sum(Total)/length(unique(Date)))
  })

#number_of_fridge_active <- reactive({df %>% group_by(week(Date))%>%filter(`week(Date)`%in%AvgUnitSold()$`week(Date)`)%>%summarise(numberFridge = length(unique(Kiosk)))})

overall2 <- reactive({df%>%group_by(week(Date))%>%summarise(AvgTotalSold=sum(Total)/length(unique(Date)))%>%
    filter(`week(Date)`%in%AvgTotalSold()$`week(Date)`)})
overallAverage2 <- reactive({overall_average = overall2()$AvgTotalSold/number_of_fridge_active()$numberFridge})

#number_of_fridge_active_fridge_type <- reactive({df %>% filter(Fridge_Type==selectedData()$Fridge_Type[1])%>% group_by(week(Date))%>%filter(`week(Date)`%in%AvgUnitSold()$`week(Date)`)%>%summarise(numberFridge = length(unique(Kiosk)))})

fridgetypeAverage2 <- reactive({df%>%group_by(week(Date))%>%filter(Fridge_Type==selectedData()$Fridge_Type[1])%>%summarise(AvgTotalSold=sum(Total)/length(unique(Date)))%>%filter(`week(Date)`%in%AvgTotalSold()$`week(Date)`)})
fridgetypeAverage21 <- reactive({overall_average = fridgetypeAverage2()$AvgTotalSold/number_of_fridge_active_fridge_type()$numberFridge})

renderPlotly(plot_ly(AvgTotalSold(), x=~`week(Date)`, y=~AvgTotalSold,type = 'scatter', mode = 'lines',name=input$Kiosk,line=list(color = '#2ca02c'))%>%add_trace(y=~overallAverage2(), name='6AM Average',mode = "lines",line=list(dash='dot',color='blue'))%>%add_trace(y=~fridgetypeAverage21(), name = paste0(selectedData()$Fridge_Type[1],' Average'), mode = 'lines', line = list(dash='dot',color='#d62728'))%>%
  layout(title = "Average Dollar Sales Per Day",
         paper_bgcolor='rgb(255,255,255)', plot_bgcolor='rgb(229,229,229)',
         xaxis = list(title = "Week",
                      gridcolor = 'rgb(255,255,255)',
                      showgrid = TRUE,
                      showline = FALSE,
                      showticklabels = TRUE,
                      tickcolor = '#2ca02c',
                      ticks = 'outside',
                      zeroline = FALSE),
         yaxis = list(title = "Average Dollar Sales $",
                      gridcolor = 'rgb(255,255,255)',
                      showgrid = TRUE,
                      showline = FALSE,
                      showticklabels = TRUE,
                      tickcolor = '#2ca02c',
                      ticks = 'outside',
                      zeroline = TRUE)))
```

### Fridge Information

```{r}

selectedData <- reactive({
  df %>% filter(df$Kiosk == input$Kiosk)
})


renderTable({
  display <- info %>% filter(Kiosk == input$Kiosk)%>%gather('Parameter','Value')
  hist <- rbind(display, c('Historical average unit price', formatC(Historical_Average_Unit_Price()$Historical_Average_Unit_Price,digits = 2, format = 'f')))
  hist[8,2] <- paste("$", hist[8,2], sep = ' ')
  hist[11,2] <- paste("$", hist[11,2], sep = ' ')
  hist
})



```   
 
### Projected Performance
    
```{r}
selectedData <- reactive({
  df %>% filter(df$Kiosk == input$Kiosk)
})

renderTable({
  monthly <- info %>% filter(Kiosk == input$Kiosk) %>% mutate('Days operational' = round(`Days Operational Per Month`),'Monthly Maintenance Fee' = `Monthly Maintenance Fee`, 'Units Sold' = round(`Days Operational Per Month`*Unit_Sold_Per_Day()$Unit_Sold_Per_Day,0), 'Projected Revenue' = round(`Units Sold`*Historical_Average_Unit_Price()$Historical_Average_Unit_Price +`Monthly Maintenance Fee`,0), 'COGS'=round(`Food COGS Margin`*`Projected Revenue`,0), 'Byte Service Fees' = `Monthly Byte Service Fees`, 'Stocking Expenses' = `Times Stocked Per Week`*15*4,'Food waste' = round(`Projected Revenue`*`Food Waste %`,0), 'Profit' = round(`Projected Revenue`-`COGS`-`Byte Service Fees`-`Stocking Expenses`,0))
  display2 <- monthly%>%select(`Days operational`:`Profit`)%>%gather('Parameter', 'Month')
  display2 <- display2 %>% mutate('Year' = `Month`*12)
  payback <- data.frame('Parameter'= 'Payback Period', 'Month' = round(monthly$`Fridge Cost`/monthly$`Profit`,2), 'Year' = round(monthly$`Fridge Cost`/monthly$`Profit`/12,2))
  payback <- rbind(display2,payback)
  for (i in 2:3){
  for (b in 3:8){
    payback[b,i] = paste("$", payback[b,i], sep = "")
  }
}
  
  payback
})
```

### Yesterday's sales by time of day

```{r}
timeofday <- reactive({
  df %>% filter(Kiosk == input$Kiosk, Date == max(df$Date)) %>%mutate(hourGroup = strftime(DateTime, format="%H")) %>% select(`Order ID`: Time, DateTime:hourGroup, Kiosk: `SLS?`)%>%group_by(hourGroup)%>%summarise(QTY = sum(Qty))%>%ungroup()
})

renderPlotly(plot_ly(timeofday(), x=~`hourGroup`, y=~QTY,name=input$Kiosk,type = 'scatter', mode = 'lines',line=list(color = '#2ca02c'))%>%
  layout(title = "Sales by Time of Day",
         paper_bgcolor='rgb(255,255,255)', plot_bgcolor='rgb(229,229,229)',
         xaxis = list(title = "Hour",
                      gridcolor = 'rgb(255,255,255)',
                      showgrid = TRUE,
                      showline = FALSE,
                      showticklabels = TRUE,
                      tickcolor = '#2ca02c',
                      ticks = 'outside',
                      zeroline = FALSE),
         yaxis = list(title = "Units Sold",
                      gridcolor = 'rgb(255,255,255)',
                      showgrid = TRUE,
                      showline = FALSE,
                      showticklabels = TRUE,
                      tickcolor = '#2ca02c',
                      ticks = 'outside',
                      zeroline = TRUE)))
```


Last Seven Days 
=======================================================================

Row 
-------------------------------------

### Units sold in the past seven days

```{r}
last_seven <- last_seven_days%>%group_by(Date, Fridge_Type)%>%summarise(QTY = sum(Qty))%>%ungroup()

last_seven %>% plot_ly(x=~Date, y=~QTY, color=~as.factor(Fridge_Type), type='scatter',mode='lines')
```

### Dollar Sales in the past seven days

```{r}
last_seven_dollar <- last_seven_days%>%group_by(Date, Fridge_Type)%>%summarise(Total = sum(Total))%>%ungroup()

last_seven_dollar %>% plot_ly(x=~Date, y=~Total, color=~as.factor(Fridge_Type), type='scatter',mode='lines')
```


Rolling Average 
=======================================================================

Row {.tabset .tabset-fade}
-------------------------------------

### 7-Day Rolling Average Unit Price

This graph shows the seven day rolling average unit price. 
```{r}
current_date  = as.Date(max(df$Date),format='%Y-%m-%d')
starting_date  = current_date-13
daterange14     = seq.Date(starting_date, current_date,by="day")


my_sales = list()
i= 1
for (d in daterange14){
  sliced = df%>%filter(Date >= d - 6 & Date <= d)
  my_sales[[i]] = sliced
  i = i+1
}

rollingAvgUnitPriceARS = data.frame(Date = daterange14)
rollingAvgUnitPriceByte = data.frame(Date = daterange14)
rollingAvgUnitPrice = data.frame(Date = daterange14)

r = 1
for(i in seq(1,14)){
  rollingAvgUnitPriceARS$AvgUnitPrice[r] = my_sales[[i]]%>%filter(Fridge_Type=='ARS')%>%summarise(AvgUnitPrice = round(sum(Total)/sum(Qty),2))
  r=r+1
}

j = 1
for(i in seq(1,14)){
  rollingAvgUnitPriceByte$AvgUnitPrice[j] = my_sales[[i]]%>%filter(Fridge_Type=='Byte')%>%summarise(AvgUnitPrice = round(sum(Total)/sum(Qty),2))
  j=j+1
}

k = 1
for(i in seq(1,14)){
  rollingAvgUnitPrice$TotalAvgUnitPrice[k] = my_sales[[i]]%>%summarise(AvgUnitPrice = round(sum(Total)/sum(Qty),2))
  k=k+1
}

rollingAvgUnitPrice$ARSAvg = rollingAvgUnitPriceARS$AvgUnitPrice
rollingAvgUnitPrice$ByteAvg = rollingAvgUnitPriceByte$AvgUnitPrice

plot_ly(rollingAvgUnitPrice, x=~daterange14,y=~TotalAvgUnitPrice, name='All Fridges', mode = 'lines', type = 'scatter', mode = 'lines',line=list(color = '#2ca02c'))%>%add_trace(y=~ARSAvg,name='ARS', mode = 'lines',type= 'scatter',mode = 'lines', line = list(color = 'red'))%>%add_trace(y=~ByteAvg,name='Byte', mode = 'lines',type= 'scatter',mode = 'lines', line = list(color = 'blue'))
```

### 7-Day Rolling Units Sold Per Day

This graph shows the seven day rolling average units sold per day. 
```{r}
rollingAvgUnitsSoldARS = data.frame(Date = daterange14)
rollingAvgUnitsSoldByte = data.frame(Date = daterange14)
rollingAvgUnitsSold = data.frame(Date = daterange14)

r = 1
for(i in seq(1,14)){
  rollingAvgUnitsSoldARS$AvgUnitsSold[r] = my_sales[[i]]%>%filter(Fridge_Type=='ARS')%>%summarise(AvgUnitsSold = round(sum(Qty)/7,2))
  r=r+1
}

j = 1
for(i in seq(1,14)){
  rollingAvgUnitsSoldByte$AvgUnitsSold[j] = my_sales[[i]]%>%filter(Fridge_Type=='Byte')%>%summarise(AvgUnitsSold = round(sum(Qty)/7,2))
  j=j+1
}

k = 1
for(i in seq(1,14)){
  rollingAvgUnitsSold$TotalAvgUnitsSold[k] = my_sales[[i]]%>%summarise(AvgUnitsSold = round(sum(Qty)/7,2))
  k=k+1
}

rollingAvgUnitsSold$ARSAvg = rollingAvgUnitsSoldARS$AvgUnitsSold
rollingAvgUnitsSold$ByteAvg = rollingAvgUnitsSoldByte$AvgUnitsSold

plot_ly(rollingAvgUnitsSold, x=~Date,y=~TotalAvgUnitsSold, name='All Fridges', mode = 'lines', type = 'scatter', mode = 'lines',line=list(color = '#2ca02c'))%>%add_trace(y=~ARSAvg,name='ARS', mode = 'lines',type= 'scatter',mode = 'lines', line = list(color = 'red'))%>%add_trace(y=~ByteAvg,name='Byte', mode = 'lines',type= 'scatter',mode = 'lines', line = list(color = 'blue'))
```

### Averge Units Sold Per Fridge (7-Day Rolling Average)

This graph shows the seven day rolling average units sold per fridge

```{r}
AvgUnitsSoldPerARSFridge = data.frame(Date = daterange14)
AvgUnitsSoldPerByteFridge = data.frame(Date = daterange14)
AvgUnitsSoldPerFridge = data.frame(Date = daterange14)


r = 1
for(i in seq(1,14)){
  AvgUnitsSoldPerARSFridge$ActiveFridge[r] = my_sales[[i]]%>%filter(Fridge_Type=='ARS')%>%summarise(activeARSFridges = length(unique(Kiosk)))
  AvgUnitsSoldPerARSFridge$UnitsSold[r] = my_sales[[i]]%>%filter(Fridge_Type=='ARS')%>%summarise(TotalUnitsSold = sum(Qty))
  AvgUnitsSoldPerARSFridge$SoldPerFridge[r] = round(AvgUnitsSoldPerARSFridge$UnitsSold[[r]]/AvgUnitsSoldPerARSFridge$ActiveFridge[[r]]/7,2)
  r=r+1
}



j = 1
for(i in seq(1,14)){
  AvgUnitsSoldPerByteFridge$ActiveFridge[j] = my_sales[[i]]%>%filter(Fridge_Type=='Byte')%>%summarise(activeByteFridges = length(unique(Kiosk)))
  AvgUnitsSoldPerByteFridge$TotalUnitsSold[j] = my_sales[[i]]%>%filter(Fridge_Type=='Byte')%>%summarise(TotalUnitsSold = sum(Qty))
  AvgUnitsSoldPerByteFridge$SoldPerFridge[j] = round(AvgUnitsSoldPerByteFridge$TotalUnitsSold[[j]]/AvgUnitsSoldPerByteFridge$ActiveFridge[[j]]/7,2)
  j=j+1
}


k = 1
for(i in seq(1,14)){
  AvgUnitsSoldPerFridge$ActiveFridge[k] = my_sales[[i]]%>%summarise(activeFridges = length(unique(Kiosk)))
  AvgUnitsSoldPerFridge$TotalUnitsSold[k] = my_sales[[i]]%>%summarise(TotalUnitsSold = sum(Qty))
  AvgUnitsSoldPerFridge$SoldPerFridge[k] = round(AvgUnitsSoldPerFridge$TotalUnitsSold[[k]]/AvgUnitsSoldPerFridge$ActiveFridge[[k]]/7,2)
  k=k+1
}


AvgUnitsSoldPerFridge$Byte = AvgUnitsSoldPerByteFridge$SoldPerFridge
AvgUnitsSoldPerFridge$ARS = AvgUnitsSoldPerARSFridge$SoldPerFridge


plot_ly(AvgUnitsSoldPerFridge, x=~Date,y=~SoldPerFridge, name='All Fridges', mode = 'lines', type = 'scatter', mode = 'lines',line=list(color = '#2ca02c'))%>%add_trace(y=~ARS,name='ARS', mode = 'lines',type= 'scatter',mode = 'lines', line = list(color = 'red'))%>%add_trace(y=~Byte,name='Byte', mode = 'lines',type= 'scatter',mode = 'lines', line = list(color = 'blue'))
```



### 7-Day Rolling Average Dollar Sales Per Day
This graph shows the seven day rolling average dollar sales per day

```{r}
rollingAvgDollarSalesARS = data.frame(Date = daterange14)
rollingAvgDollarSalesByte = data.frame(Date = daterange14)
rollingAvgDollarSales = data.frame(Date = daterange14)

r = 1
for(i in seq(1,14)){
  rollingAvgDollarSalesARS$AvgDollarSales[r] = my_sales[[i]]%>%filter(Fridge_Type=='ARS')%>%summarise(AvgDollarSales = round(sum(Total)/7,2))
  r=r+1
}

j = 1
for(i in seq(1,14)){
  rollingAvgDollarSalesByte$AvgDollarSales[j] = my_sales[[i]]%>%filter(Fridge_Type=='Byte')%>%summarise(AvgDollarSales = round(sum(Total)/7,2))
  j=j+1
}

k = 1
for(i in seq(1,14)){
  rollingAvgDollarSales$TotalAvgDollarSales[k] = my_sales[[i]]%>%summarise(AvgDollarSales = round(sum(Total)/7,2))
  k=k+1
}

rollingAvgDollarSales$ARSAvg = rollingAvgDollarSalesARS$AvgDollarSales
rollingAvgDollarSales$ByteAvg = rollingAvgDollarSalesByte$AvgDollarSales

plot_ly(rollingAvgDollarSales, x=~Date,y=~TotalAvgDollarSales, name='All Fridges', mode = 'lines', type = 'scatter', mode = 'lines',line=list(color = '#2ca02c'))%>%add_trace(y=~ARSAvg,name='ARS', mode = 'lines',type= 'scatter',mode = 'lines', line = list(color = 'red'))%>%add_trace(y=~ByteAvg,name='Byte', mode = 'lines',type= 'scatter',mode = 'lines', line = list(color = 'blue'))
```

### Averge Dollar Sales Per Fridge (7 day Rolling Average) 

This graph shows the seven day rolling average dollar sales per fridge

```{r}
AvgDollarSalesPerARSFridge = data.frame(Date = daterange14)
AvgDollarSalesPerByteFridge = data.frame(Date = daterange14)
AvgDollarSalesPerFridge = data.frame(Date = daterange14)


r = 1
for(i in seq(1,14)){
  AvgDollarSalesPerARSFridge$ActiveFridge[r] = my_sales[[i]]%>%filter(Fridge_Type=='ARS')%>%summarise(activeARSFridges = length(unique(Kiosk)))
  AvgDollarSalesPerARSFridge$dollarSales[r] = my_sales[[i]]%>%filter(Fridge_Type=='ARS')%>%summarise(TotalDollarSales =sum(Total))
  AvgDollarSalesPerARSFridge$SoldPerFridge[r] = round(AvgDollarSalesPerARSFridge$dollarSales[[r]]/AvgDollarSalesPerARSFridge$ActiveFridge[[r]]/7,2)
  r=r+1
}



j = 1
for(i in seq(1,14)){
  AvgDollarSalesPerByteFridge$ActiveFridge[j] = my_sales[[i]]%>%filter(Fridge_Type=='Byte')%>%summarise(activeByteFridges = length(unique(Kiosk)))
  AvgDollarSalesPerByteFridge$dollarSales[j] = my_sales[[i]]%>%filter(Fridge_Type=='Byte')%>%summarise(TotalDollarSales = sum(Total))
  AvgDollarSalesPerByteFridge$SoldPerFridge[j] = round(AvgDollarSalesPerByteFridge$dollarSales[[j]]/AvgDollarSalesPerByteFridge$ActiveFridge[[j]]/7,2)
  j=j+1
}


k = 1
for(i in seq(1,14)){
  AvgDollarSalesPerFridge$ActiveFridge[k] = my_sales[[i]]%>%summarise(activeFridges = length(unique(Kiosk)))
  AvgDollarSalesPerFridge$dollarSales[k] = my_sales[[i]]%>%summarise(TotalDollarSales = sum(Total))
  AvgDollarSalesPerFridge$SoldPerFridge[k] = round(AvgDollarSalesPerFridge$dollarSales[[k]]/AvgDollarSalesPerFridge$ActiveFridge[[k]]/7,2)
  k=k+1
}


AvgDollarSalesPerFridge$Byte = AvgDollarSalesPerByteFridge$SoldPerFridge
AvgDollarSalesPerFridge$ARS =AvgDollarSalesPerARSFridge$SoldPerFridge


plot_ly(AvgDollarSalesPerFridge, x=~Date,y=~SoldPerFridge, name='All Fridges', mode = 'lines', type = 'scatter', mode = 'lines',line=list(color = '#2ca02c'))%>%add_trace(y=~ARS,name='ARS', mode = 'lines',type= 'scatter',mode = 'lines', line = list(color = 'red'))%>%add_trace(y=~Byte,name='Byte', mode = 'lines',type= 'scatter',mode = 'lines', line = list(color = 'blue'))
```

Time of Day 
======================================================================= 
This page shows you last seven days unit sales breakdown by time of day 

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Product Category  

```{r}

top_date  = as.Date(max(df$Date),format='%Y-%m-%d')
low_date  = top_date-6
dts_      = seq.Date(low_date, top_date,by="day")
daterange1 = dts_[rev(order(as.Date(dts_, format = "%m-%d-%Y")))]

dff <- df %>% filter(Date %in% daterange1) %>% mutate(hourGroup = strftime(DateTime, format="%H")) %>% select(`Order ID`: Time, DateTime:hourGroup, Kiosk: `SLS?`)

df1 <- dff %>% group_by(hourGroup, `Product Category`)%>%summarise(QTY = sum(Qty))%>%ungroup()
df1 %>% plot_ly(x=~hourGroup, y=~QTY,color=~`Product Category`, type = 'scatter', mode= "lines")%>%
  layout(xaxis = list(title = 'Time of Day (Hour)'))

```

### Fridge Type

```{r}

df2 <- dff %>% filter(Date %in% daterange1)%>% group_by(hourGroup, Fridge_Type)%>%summarise(QTY = sum(Qty))%>%ungroup()
df2 %>% plot_ly(x=~hourGroup, y=~QTY,color=~Fridge_Type, type = 'scatter', mode= "lines")%>%
  layout(xaxis = list(title = 'Time of Day (Hour)'))

```

### Kiosk Segment

```{r}
df3 <- dff %>% filter(Date %in% daterange1)%>% group_by(hourGroup, Kiosk_Segment)%>%summarise(QTY = sum(Qty))%>%ungroup()
df3 %>% plot_ly(x=~hourGroup, y=~QTY,color=~Kiosk_Segment, type = 'scatter', mode= "lines")%>%
  layout(xaxis = list(title = 'Time of Day (Hour)'))
```

### Product

```{r}
df6 <- dff %>% filter(Date %in% daterange1)%>% group_by(hourGroup, Product)%>%summarise(QTY = sum(Qty))%>%ungroup()
df6 %>% plot_ly(x=~hourGroup, y=~QTY,color=~Product, type = 'scatter', mode= "lines")%>%
  layout(xaxis = list(title = 'Time of Day (Hour)'))
```


About 
======================================================================= 


***

The ‘Sales’ tab is showing you sales summary and fridge P/L analysis by individual fridges.

	- ‘Days active’: the number of days a fridge has been active. 
	
	- ‘Units Sold to Date’: the total number of products sold at the kiosk you selected to date.
	
	- ‘Dollar Sales to Date’: the total dollar sales at the location selected since inception. 
	
	- ‘Historical Units Sold Per Day (Since Inception)’: average units sold per day since inception (total units sold to date/days active).
	
	- ‘Historical Average Unit Price Since Inception’: total dollar sales/total units sold.
	
	- ‘Average Daily Units Sold Last Week’: average units sold per day for the last 7 days. Note that if the fridge has not been active longer than 7 days this data is not accurate. 
	
	- ‘Average Daily Dollar Sales Past Week’: average dollar sales per day for the last 7 days. Note that if the fridge has not been active longer than 7 days this data is not accurate. 
	
	- ‘Average Unit Price Past 7 Days’: average unit price within the last 7 days. Note that if the fridge has not been active longer than 7 days this data is not accurate. 
	
***

The 'Rolling Average' tab is showing you 7-day rolling average data over a 14-day time span (2 weeks)


  